xsface - file length sanity checking

### 2018-03-13 analysis-validation/frame_validation/check_frame_counts_post_detection.Rmd
expand sanity check frame scripts

```{r}
library(tidyverse)
library(knitr)
```

Load data
```{r}
ffprobe_frame_counts <- read_csv("data/video_stats/ffprobe_frame_count.csv")
extracted_frame_counts <- read_csv("data/video_stats/extracted_frame_count.csv")
mtcnn_data <- read_csv("data/final_output/mtcnn_face_detections.csv")
# openpose_data 
```

Check ffprobe results against actual extracted frames
```{r}
ffprobe_frame_counts %>%
  all.equal(extracted_frame_counts)
```

>>>>

```{r}

library(tidyverse)
library(knitr)

Load data
```{r}
ffprobe_frame_counts <- read_csv("../../data/video_stats/ffprobe_frame_count.csv")
extracted_frame_counts <- read_csv("../../data/video_stats/extracted_frame_count.csv")
mtcnn_data <- read_csv("../../data/final_output/mtcnn3.csv")
# openpose_data 
```

Check ffprobe results against actual extracted frames
```{r}
s
```

### 2018-03-13 analysis-validation/length_sanity_check.Rmd
expand sanity check frame scripts

---
title: "xsface - file length sanity checking"
author: "Mike Frank"
date: "July 11, 2016"
output:
  html_document:
  toc: true
---

@@

1. source files for movies
2. demographic sheet (containing session lengths)
3. detector outputs

```{r}
rm(list=ls())
library(readr)
library(magrittr)
library(dplyr)
library(lubridate)
```

read in lengths on movies

```{r}
demo <- read_csv("../data/demographics/demographics.csv")
movies <- read_csv("../data/video_stats/new_movie_lengths.csv") 
dets <- read_csv("../data/final_output/mtcnn3.csv")
```

@@

# standardize
dets$frame=as.numeric(dets$frame)
dets$subid=dets$video

det.lens <- dets %>%
  group_by(subid) %>%
  summarise(frames_dets = max(frame))
```

@@

```{r}
all_data <- left_join(demo, movies) %>%
  left_join(det.lens) %>%
  select(subid, recorded_len, last_frame_movie, length_movie, frames_dets) %>%
  mutate(det_frame_err = abs(last_frame_movie - frames_dets) > 100,
         demo_time_err = abs(recorded_len - length_movie) > 1) %>%
  data.frame
```

@@

Explanations of discrepancies:

>>>>

---
title: "xsface - file length sanity checking"
author: "Mike Frank, continued by Bria Long & Alessandro Sanchez"
date: "July 11, 2016"
output:
  html_document:
  toc: true
---

@@

1. source files for movies
2. demographic sheet (containing session lengths)
3. detector outputs (MTCNN/ OpenPose)
4. timing outputs from ffprobe

```{r}
rm(list=ls())
library(readr)
library(magrittr)
library(dplyr)
library(lubridate)
library(stringr)

```

read in lengths on movies, demographics, detections, and frame time outputs

```{r}
demo <- read_csv("../data/demographics/demographics.csv")
movies <- read_csv("../data/video_stats/new_movie_lengths.csv") 
MTCNN <- read_csv("../data/final_output/mtcnn3.csv")
openPose <- read_csv("../data/final_output/openpose_results_truncated_2.csv")
frameTimes <- read_csv("../data/video_stats/frametimechecks_showframes.csv")
```

@@

# standardize
MTCNN$frame=as.numeric(MTCNN$frame)
MTCNN$subid=MTCNN$video
openPose$frame=as.numeric(openPose$frame)
openPose$subid=openPose$name

## get out max frame
MTCNN.lens <- MTCNN %>%
  group_by(subid) %>%
  summarise(frames_dets_mtcnn = max(frame))

openPose.lens <- openPose %>%
  group_by(subid) %>%
  summarise(frames_dets_op = max(frame))

## get frames from frame time output (ffprobe)
frameTimes <- frameTimes %>%
  mutate(last_frame_times = last.frame) %>%
  mutate(subid = str_replace_all(subid,"-","_")) %>%
  mutate(subid = str_sub(as.character(subid),start=1,end=7))

```

@@

```{r}
all_data <- left_join(demo, movies) %>%
  left_join(MTCNN.lens) %>%
  left_join(openPose.lens) %>%
  left_join(frameTimes) %>%
  select(subid, recorded_len, length_movie, last_frame_movie, last_frame_times, frames_dets_mtcnn, frames_dets_op) %>%
  mutate(det_frame_err = abs(last_frame_movie - frames_dets_mtcnn) > 100,
         demo_time_err = abs(recorded_len - length_movie) > 1,
         frame_time_diff = last_frame_times - frames_dets_mtcnn) %>%
  data.frame

sum(all_data$frame_time_diff)
```

@@

XS_1229 has been trimmed (headcam came off) and therefore there are different movie lenghts.

=====

Mike's notes (Explanations of old discrepancies :)
